---
title: "H4"
author: "grienne"
date: "October 12, 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Foundation}
library(readxl)
library(knitr)
library(ggplot2)
library(dplyr)
library(ResourceSelection)
library(generalhoslem)

dat <- read_excel("oct_11_2018_h4_table_7_18.xlsx")

dat_try <- read_excel("dat_comp.xlsx")

names(dat) <- c('wais', 'symptom')

```

---

Question 1

A. For the simple logistic model pii = ebetai/(1 + ebetai), show that if there is no diﬀerence between the exposed (b1)
    and not exposed groups (b2) (i.e., beta1 = beta2), then phi = 1
      
       
    
          Set phi = 1 = [ pi1/ (1 − pi2) ] / [ pi2 (1 − pi1) ] =>
                
                Cross Multiply   
                   [ pi1/ (1 − pi2) ] = [ pi2 (1 − pi1) ]
                  Multiply Out
                    pi1 − pi1pi2 = pi2 − pi1pi2
                    Algebra
                        pi1 = pi2
                      Express
                        ebeta1/(1 + ebeta1) =  ebeta2/(1 + ebeta2)
                        Cross Multiply
                          ebeta1*(1 + ebeta2) =  ebeta2*(1 + ebeta1)
                          Multiply Out 
                            ebeta1 + ebeta1 * ebeta2) =  ebeta2 + ebeta1* ebeta2
                            Algebra
                              ebeta1 = ebeta2
                              Log
                                beta1 = beta2 if and only if beta1 = beta2
                          
      
B. Consider J 2 × 2 tables like Table 7.13, one for each level xj of a factor, such as age group, with j = 1,...,J. 
    For the logistic model
      piij = exp(alphai + betaixj) / 1 + exp(alphai + betaixj), i = 1,2, j = 1,...,J.
        Show that log phi is constant over all tables if beta1 = beta2   

              if phi = exp(pi1 - pi2)
                then   log phi = (alpha1 - alpha2) + xj(beta1 - beta2) if beta1 = beta2
        
        log of phi = [logpi1-logpi2]2 let x1=alpha1+beta1*Xj and let x2= alpha2+beta2*Xj  
            2[Log (exp(x1)/(1+exp(x1))-Log (exp(x2)/(1+exp(x2)) => 4[x1-x2]
                log phi = 4[xj(beta1-beta2)+alpha1-alpha2] if beta1=beta2 it is a constant        
        
---

```{r Question 2}
#Problem 2

#(a)Confirm the first 4 columns of Table 7.9.
 
count<-aggregate( data=dat,symptom~wais,length)
count2<-aggregate( data=dat,symptom~wais,sum)

names(count) <- c("wais", "total_symp_count")

tbl <- merge(count, count2, by ='wais', all = T)

tbl$no_symp<- (tbl$total_symp_count - tbl$symptom)

names(tbl) <- c("wais", "total_symp_count", "yes_symp", "no_symp") 
 
#calculate prop
tbl$prop<- (tbl$yes_symp/tbl$total_symp_count)
 
#(b)Confirm the estimation of the B's and corresponding standard errors
p2_fit <- glm(prop~wais, data = tbl,family = binomial(link="logit"))
summary(p2_fit)
coef(p2_fit)
 
#(c)Verify the Hosmer-Lemeshow test statistic

pfit <- glm(symptom~wais, data = dat,family = binomial(link="logit"))
          

h1 <- logitgof(dat$symptom, fitted(pfit), g=3)
h1

#(d) Replicate the plot in Figure 7.5.

p <- ggplot(data = tbl, aes(x=wais, y=prop))
p + geom_point() + geom_smooth(method = "loess", se = FALSE) 

#(e) Interpret
  #With increasing WAIS scores, chances of senility are reduced. 

```


---

Question 3

Git ID - grienne

---

---

Question 4

Certificate also stored in git
#Git-Link: https://github.com/grienne/bst_oct_11_2018.git

Completion Date 26-Aug-2018
Expiration Date 25-Aug-2021
Record ID 28316665
#Verify at www.citiprogram.org/verify/?w493f4f53-6552-4fb1-8285-a171d8d5bba0-28316665
---